---
title: "SAR exercicio pratico"
author: "Alexandre Camargo Martensen"
date: '`r Sys.time()`'
output: 
  html_document:
     keep_md: yes
     toc: TRUE
     toc_depth: 3
  keep_md: TRUE
---

# SAR

Adapted from <a href="http://datacarpentry.org/semester-biology/">"Data Carpentry for Biologists"</a> 

http://datacarpentry.org/semester-biology/exercises/Higher-order-functions-species-area-relationship-R/

Also see: <a href="https://onlinelibrary.wiley.com/doi/full/10.1111/j.1365-2699.2008.02038.x">Dengler 2009</a>

## Models

Potência: S = b0 * A^b1

Potência-quadrada: S = 10^(b0 + b1 * log(A) + b2 * log(A)^2)

Logarítmico: S = b0 + b1 * log(A)

Michaelis-Menten: S = b0 * A / (b1 + A)

Lomolino: S = b0 / (1 + b1^log(b2/A))

_______

## The code 

### Pck

```{r}
library(knitr) #Only for visualization
```

### Data

```{r}
download.file("http://datacarpentry.org/semester-biology/data/sar-areas.csv", "sar-areas.csv")
areas<-read.csv("sar-areas.csv", header=FALSE)
```

Areas
```{r}
areas
```

<a href="https://onlinelibrary.wiley.com/doi/10.1111/j.1365-2699.2010.02322.x">artigo Dengler and Oldeland (2010)</a>
```{r}
download.file("http://datacarpentry.org/semester-biology/data/sar-model-data.csv", "sar-model-data.csv")
parametros<-read.csv("sar-model-data.csv", header=FALSE)
colnames(parametros)<-c("modelos", "b0", "b1", "b2")
```

Checking the parameters
```{r}
kable(parametros)
```

### Functions
```{r}
potencia<-function(b0, Areas, b1){
  S = b0 * Areas^b1
  return(S)
}

pot_quadrada<-function(b0, b1, Areas, b2){
  S = 10^(b0 + b1 * log10(Areas) + b2 * log10(Areas)^2)
  return (S)
}

loga<-function(b0, b1, Areas){
  S = b0 + b1 * log10(Areas)
  return (S)
}

MM<-function(b0, Areas, b1){
  S = b0 * (Areas / (b1 + Areas))
  return (S)
}

Lomo<-function(b0, b1, b2, Areas){
  S = b0/(1 + b1^(log10(b2/Areas)))
  return (S)
}
```

### Results

Calculations
```{r}
mod1<-potencia(parametros[1,"b0"], areas, parametros[1,"b1"])
mod2<-pot_quadrada(parametros[2,"b0"], parametros[2,"b1"], areas, parametros[2,"b2"])
mod3<-loga(parametros[3,"b0"], parametros[3,"b1"], areas)
mod4<-MM(parametros[4,"b0"], areas, parametros[4,"b1"])
mod5<-Lomo(parametros[5,"b0"], parametros[5,"b1"], parametros[5,"b2"], areas)
```

Organizing the results
```{r}
mods<-cbind(mod1, mod2, mod3, mod4, mod5)
colnames(mods)<-c("Power", "PowerQuadratic", "Logarithmic", "Michaelis-Menten", "Lomolino")
```

Checking results
```{r}
kable(mods)
```

Checking the average and comparing with the one obtained from  <a href="http://datacarpentry.org/semester-biology/solutions/Higher-order-functions-species-area-relationship-R.txt">the site</a>
```{r}
download.file("http://datacarpentry.org/semester-biology/solutions/Higher-order-functions-species-area-relationship-R.txt", "Higher-order-functions-species-area-relationship-R.txt")

res.comp<-read.table("Higher-order-functions-species-area-relationship-R.txt", header=TRUE, sep=",")

resultados<-cbind(areas, rowMeans(mods), res.comp)
```

Checking the averages and comparing with the ones from the site.
```{r}
kable(resultados)
```

#Results are different

